---
title: "Problem Set #X"
subtitle: "BST 258: Causal Inference -- Theory and Practice"
author: "[Your Name Here]"
date: ""
format:
  pdf:
    documentclass: scrartcl
    papersize: letter
    fontsize: 11pt
    geometry:
      - margin=1in
      - heightrounded
    number-sections: false
    colorlinks: true
    link-citations: true
    callout-appearance: simple
    callout-icon: false
    # figure options
    fig-width: 6
    fig-asp: 0.618
    fig-cap-location: bottom
    # code block options
    code-line-numbers: false
    code-block-bg: false
    highlight-style: nord
bibliography: refs.bib
---

```{r}
#| echo: false
#| message: false
#| label: global-setup
# NOTE: The immediately following line loads an renv environment located at the
#       nearest "top-level" directory, as marked by a `.here` file, which is
#       located by the here::here() function. This would be a useful tool if,
#       say, this template.qmd file was not located at the top-level directory.
#       Here, renv should activate automatically when this file is opened.
#renv::load(here::here())
library(here)
```

\footnotesize
**Problem set policies:** Please provide concise, clear answers for each
question. Note that only writing the result of a calculation without
explanation is not sufficient. For problems involving \textsf{R}, include the
code in your solution, along with any figures or tables.

Please submit your problem set via Canvas in PDF, alongside the corresponding
\textsf{Quarto} (`.qmd`) source file.

We encourage you to discuss problems with other students, but you must
write your final answer in your own words. Solutions prepared "in
committee" are not acceptable. If you do collaborate with classmates on a
problem, please list your collaborators on your solution. Similarly, while you
may find the use of ChatGPT and related tools helpful, disclosing your use of
them is required to adhere to academic/intellectual honesty.

::: {.callout-warning title="Coding Standards"}
Make sure to write code that is modular and reusable, making use of functions
or classes as necessary. Make sure to use variable names that are descriptive
--- that is, human parse-able (e.g., not `x` or `this_var`) --- while favoring
conciseness. Write brief documentation for any functions or classes as well as
any unit tests necessary you deem necessary to ensure that your code is working
as expected. Finally, make to set a seed for the PRNG so that any random aspects
of your analysis (e.g., Monte Carlo simulation experiments, sample-splitting)
are reproducible.
:::

Remember that \textsf{Quarto} extends markdown, which supports \LaTeX for
typesetting equations, and also allows for code and analytic results to be
interspersed in a single document, consistent with literate programming
principles.

Put your answer in ["callout"
blocks](https://quarto.org/docs/authoring/callouts.html) like the following

:::{.callout-note title="Answer"}
Here is my answer. The logic follows, but first I will typeset a definition
to clarify my point: $P_n f(X) = \frac{1}{n} f(X_i)$.

I can also create "displayed equations," using, e.g., the `align` environment,
\begin{align*}
  L &\sim \text{Unif}(-1, 1) \\
  A &\sim \text{Bern}(0.5) \\
  Y &\sim \text{N}(\mu = 2 A + 0.5 L, \sigma = 1)
\end{align*}
:::

You can also write and run \textsf{R} code. As an example, below, we load two
packages, `data.table` and `tidyverse`, and set a seed for the PRNG.

```{r}
#| label: example-code
library(data.table)
library(tidyverse)
set.seed(11249)
```

You may also cite sources from the `refs.bib` file, e.g., @hernan2023causal.
\normalsize

{{< pagebreak >}}



## Question 1

Start answer here


{{< pagebreak >}}


## Question 2

Start answer here


{{< pagebreak >}}


## Question 3

Start answer here


{{< pagebreak >}}


## References

::: {#refs}
:::

